Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

```{r fig.height=4, fig.width=5}
#| echo: false
#| message: false
#| label: fig-gender-strip-search
#| fig-cap: Gender Identities and Police Strip Search Per Arrest in Toronto, 2020-2021

>>>>

```{r fig.height=4, fig.width=5, fig.align='center'}
#| echo: false
#| message: false
#| label: fig-gender-strip-search
#| fig-cap: Gender Identities and Police Strip Search Per Arrest in Toronto, 2020-2021
